Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2018-11-14 papers/paper/paper.tex
Add simulation printing mode to generate a new data file with tx, ty, motor and binding angle info in bothbound. This is for a new figure.

-Dynein's two feet take different steps according to yildiz/qiu
-Carter 2008 says that dynein's MTBD decides directionaolity, whereas Redwine 2012 thinks its linker motion (clarify)
-Imai 2015 has lots to say criticizing the step length studies of qiu/yildiz and have something to say about domain movement MT search
-Someone else referred to the Cianfrocco model, so maybe it's a good one to refer to (well accepted)
-The winch model is also referred to as the

>>>>

-Dynein's two feet take different steps according to yildiz/qiu
-Carter 2008 says that dynein's MTBD decides directionaolity, whereas Redwine 2012 thinks its linker motion (clarify)
-Imai 2015 has lots to say criticizing the step length studies of qiu/yildiz and have something to say about domain movement MT search
-Someone else referred to the Cianfrocco model, so maybe it's a good one to refer to (well accepted)
-It's important that our model doesn't have the powerstroke mechanism in, only observations from experiment
